\documentclass{article}

\usepackage[margin=1in]{geometry}

\usepackage{epsfig,amssymb,amsmath,multicol,xcolor,enumerate,systeme}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}

\newcommand{\x}{\mathbf{x}}
\newcommand{\y}{\mathbf{y}}
\renewcommand{\b}{\mathbf{b}}
\renewcommand{\u}{\mathbf{u}}
\renewcommand{\v}{\mathbf{v}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\e}{\mathbf{e}}
\newcommand{\0}{\mathbf{0}}

\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

\DeclareMathOperator{\Nul}{Nul}
\DeclareMathOperator{\Col}{Col}
\DeclareMathOperator{\Row}{Row}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\Span}{Span}
\DeclareMathOperator{\proj}{proj}
\DeclareMathOperator{\range}{range}

\begin{document}

\title{Math 401 - Homework \#4\\ Least-Squares and Curve Fitting\\ due on Gradescope by 9am Friday, October 1}
\author{}
\date{}
\maketitle

\noindent \textbf{Instructions:} Work through the problems below.  Write down your solutions on paper.  You can use MATLAB for computations unless the problem says ``Must do all computations by hand."  For problems in which you use MATLAB to do computations, I do not want you to turn in any MATLAB code.  You need to clearly present all steps of your solution so that I can follow your thought process without guessing what you are thinking (try writing in complete sentences.)

\begin{enumerate}
	\item Do Exercise 3.1 from the text.
	

	
	\item Do Exercise 3.13 from the text.  (It should say ``Assuming it is unique" rather than ``Assuming it exists".)
	
	\item $\begin{bmatrix}
	3 & -1 & 4\\
	0 & 2 & 1\\
	-2 & 2 & -2\\
	1 & -3 & 0
	\end{bmatrix}\begin{bmatrix}
	x_1\\ x_2\\ x_3
	\end{bmatrix} = \begin{bmatrix}
	1\\ 0\\ -1\\ 0
	\end{bmatrix}$ \begin{enumerate}
		\item Find all least-squares solutions to the above linear system (be careful, there is more than one least-squares solution.)  Present your answers in parametric vector form.
		\item Give two different least-squares solutions, and compute the least-squares error for each one.
	\end{enumerate}
	
	\item Consider the following system of linear equations, which has $n$ equations and just one variable $x$.
	\[\left\{\begin{array}{l}
	x = b_1\\
	x = b_2\\
	\quad \vdots \\
	x = b_n
	\end{array}\right.\]
	\begin{enumerate}
		\item Express this linear system in the form $A\x = \b$.  Clearly identify $A$, $\x$, and $\b$.
		\item Clearly, this is an inconsistent linear system (unless all $b_i$'s are equal).  Find the least-squares solution.  (Does the answer make sense intuitively?  The least-squares solution is the value of $x$ which tries its best to satisfy all equations at once.)
	\end{enumerate}

	\item \textbf{(Must do all computations by hand.)} Do Exercise 4.1 from the text.
	
	\item Suppose we want to find a line $y = \beta_0 + \beta_1x$ that best fits the following data:\qquad $\begin{array}{r|r}
	x & y\\
	\hline
	0 & 1.15\\
	1 & 1.56\\
	2 & 2.69\\
	3 & 3.45\\
	4 & 4.10\\
	5 & 5.00\\
	6 & 5.89\\
	7 & 7.03\\
	8 & 7.77\\
	9 & 8.17
	\end{array}$
	\begin{enumerate}
		\item Write down the system of equations that we need to find a least-squares solution to in order to find the best fit line.
		\item Find the line $y = \beta_0 + \beta_1x$ that best fits the data.
		\item Use your line to predict the value of $y$ when $x=15$.
	\end{enumerate}

	\item Consider the following data set:\qquad $\begin{array}{r|r}
	x & y\\
	\hline
	-7 & 69.4\\
	-5 & 42.2\\
	-3 & 22.3\\
	-1 & 10.4\\
	1 & 6.0\\
	3 & 9.0\\
	5 & 20.1\\
	7 & 38.5
	\end{array}$
	\begin{enumerate}
		\item \begin{enumerate}
			\item Find the least-squares line $y = \beta_0 + \beta_1 x$ that best fits this data.
			\item Find the associated least-squares error.
		\end{enumerate}
		\item \begin{enumerate}
			\item Find the least-squares parabola $y = \gamma_0 + \gamma_1 x + \gamma_2 x^2$ that best fits this data.
			\item Find the associated least-squares error.
		\end{enumerate}
		\item Provide a picture of a graph of the data points, the least-squares line, and the least-squares parabola (all in the same graph).  You can either print out a plot made in MATLAB (or something else), or you can create the graph using technology and then sketch it yourself on paper (it doesn't have to be perfect).
	\end{enumerate}

	\item Do Exercise 4.4 from the text.  (For the plot, either include a MATLAB printout or draw a rough sketch on paper of a plot you create in MATLAB).
	
	\item Do Exercise 4.6 from the text.  (Each triple is an $(x,y,z)$.  You are trying to fit $z = Ax^2 + By^2$ to the data.)
	

	
	\item Do Exercise 4.13 from the text.

\end{enumerate}

\end{document}